\LARGE \bf Mixed Non-Bayesian and DeGroot Learning

### 2012-12-11 docs/paper.tex
Initial add of simulation graphs to paper
Two column format, changes to the way images are displayed.
Added some captions and citations

\documentclass[a4paper,12pt]{article}
\usepackage{amsmath} % For 'cases' curly brace
\usepackage{amsfonts} % For bold number set font
\usepackage{graphicx}
\usepackage[font=bf]{caption}
\begin{document}
\title{Mixed Non-Bayesian and DeGroot Learning}
\author{Pedro d'Aquino\\pdaquino@umich.edu \and Dan Clark\\ddclark@umich.edu}
\date{December 11, 2012}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.8]{trapezoidalDistribution}
\caption{Trapezoidal Probability Distribution}
\end{figure}

@@

% @todo[DDC] More detail for derivation/explanation of likelihood?
The likelihood function $\ell_i(s_i|\theta_k)$ can be obtained from the probability distribution function represented by the belief state $\theta_k$.  As an example, for the trapezoidal distribution described in section~\ref{sec:trapezoidal_distribution}, the likelihood function would be

@@

\section{Simulation}

@@

\subsection{Node Ratio vs. Convergence Time}
\label{sec:simulation}

In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.  To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian received any signals; the other 50\% needed to rely completely on learning from their neighbors.  Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.

% Graph here

The data show a somewhat counterintuitive result: the presence of naive DeGroot nodes actually tends to accelerate the speed of convergence.  Further investigation showed this to be a result of the process used to convert DeGroot belief to Non-Bayesian belief.  The conversion method of section~\ref{sec:likelihood_metric} tends to result in a belief distribution that is heavily skewed to a single $\theta_i$.  This relative ``certainty'' of the DeGroot nodes is picked up by their Non-Bayesian neighbors, bringing them more quickly to convergence.

% Graph here

@@

We also evaluated time to convergence versus graph size for several network types.  These simulations were performed with a ratio of 0.8 Non-Bayesian to DeGroot nodes, where 60\% of Non-Bayesian nodes received signals from the true probability distribution and 40\% had to rely completely on information from neighbors.

% Graph here

Time required for convergence appears to be linear with respect to the number of nodes in the graph.

>>>>

%\documentclass[a4paper,12pt]{article}
\documentclass[letterpaper, 10pt, conference]{ieeeconf}
\usepackage{amsmath} % For 'cases' curly brace
\usepackage{amsfonts} % For bold number set font
\usepackage{graphicx}
\usepackage[font=bf]{caption}
\begin{document}
\title{\LARGE \bf
Mixed Non-Bayesian and DeGroot Learning
}
\author{Pedro d'Aquino\\pdaquino@umich.edu \and Dan Clark\\ddclark@umich.edu}
\date{December 11, 2012}

@@

\begin{figure}[h]
\centering
%\includegraphics[scale=0.8]{trapezoidalDistribution}
\includegraphics[width=0.48\textwidth]{trapezoidalDistribution}
\caption{Trapezoidal Probability Distribution}
\label{fig:trapezoidal}
\end{figure}

@@

The likelihood function $\ell_i(s_i|\theta_k)$ can be obtained from the probability distribution function represented by the belief state $\theta_k$.  As an example, for the trapezoidal distribution described in section~\ref{sec:trapezoidal_distribution}, the likelihood function would be

@@

\section{Simulation}
\label{sec:simulation}

@@

\subsection{Node Ratio vs. Convergence Time}
\label{sec:node_ratio_vs_convergence_time}

In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.  This simulation was performed for a several graph types: Barabasi-Albert preferential attachment~\cite{Barabasi}, Kleinberg small-world~\cite{KleinbergSmallWorld}, Eppstein power law~\cite{Eppstein}, and the complete graph.  To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian received any signals; the other 50\% needed to rely completely on learning from their neighbors.  Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.

\begin{figure*}[t]
%\hspace*{0.1in}
%\centerline{\includegraphics[scale=0.8]{figures/nb_ratio}}
\centering
\includegraphics[width=0.9\textwidth]{figures/nb_ratio}
\caption{Time to convergence decreases as the ratio of Non-Bayesian to DeGroot nodes decreases}
\label{fig:nb_ratio}
\end{figure*}

The results, shown in figure~\ref{fig:nb_ratio}, are somewhat counterintuitive: the presence of naive DeGroot nodes actually tends to accelerate the speed of convergence.  Further investigation showed this to be a result of the process used to convert DeGroot belief to Non-Bayesian belief.  The conversion method of section~\ref{sec:likelihood_metric} tends to result in a belief distribution that is heavily skewed to a single $\theta_i$.  This relative ``certainty'' of the DeGroot nodes is picked up by their Non-Bayesian neighbors, bringing them more quickly to convergence.

We can see this process in more detail in figure~\ref{fig:dg_faster}.

\begin{figure}[th]
%\hspace*{0.1in}
%\centerline{\includegraphics[scale=0.8]{figures/dg_faster}}
\centering
\includegraphics[width=0.48\textwidth]{figures/dg_faster}
\caption{@todo[DDC]}
\label{fig:dg_faster}
\end{figure}

@@

We also evaluated time to convergence versus graph size for each of the network types tested in section~\ref{sec:node_ratio_vs_convergence_time}.  These simulations were performed with a ratio of 0.8 Non-Bayesian to DeGroot nodes, where 60\% of Non-Bayesian nodes received signals from the true probability distribution and 40\% had to rely completely on information from neighbors.

\begin{figure*}[h]
%\hspace*{0.1in}
%\centerline{\includegraphics[scale=0.8]{figures/convergence_time}}
\centering
\includegraphics[width=.9\textwidth]{figures/convergence_time}
\caption{Time to convergence increases linearly with the size of the graph}
\label{fig:convergence_time}
\end{figure*}

The results, shown in figure~\ref{fig:convergence_time}, show that time required for convergence appears to be linear with respect to the number of nodes in the graph.
